%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CURRENT AFFILIATIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  \textbf{\href{https://rise.org.cy}{RISE}, Cyprus}
  \begin{outerlist}
  \item[\textbf{Research Centre on Interactive Media, Smart Systems and Emerging Technologies}]
  \item[\textit{Researcher}] \hfill \textbf{2019--}
  \end{outerlist}
  \vspace{15pt}
  
  \textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
  \item[\textbf{\href{https://bradlove.org/}{Prof. Bradley C. Love's Lab}}] 
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}

  \end{outerlist}
  \vspace{15pt}
  
  
  \textbf{School of Mathematics, Computer Science and Engineering, City, \newline University of London, UK}
  \begin{outerlist}
  \item[\textbf{\href{https://cit-ai.net}{CitAI, Artificial Intelligence Research Centre}}]
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}
  \end{outerlist}

  
\textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
  \item[\textbf{\href{https://bradlove.org/}{Prof. Bradley C. Love's Lab}}] 
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}
    \begin{innerlist}
    \item  Serving on hiring committees for postdoctoral fellows.
    \item  Assisting with Cognitive and Decision Sciences M.Sc.
    \item  Mentoring students and postdocs.

  \end{innerlist}
  \end{outerlist}
  \vspace{15pt}
  
      \item  Organised training courses for: git, continuous integration, module testing.
    \item  Served on hiring committees for postdoctoral fellows.
    \item  Assisted with Cognitive and Decision Sciences M.Sc.
    \item  Mentored Ph.D. and M.Sc. students (CSML and DSML M.Sc.s)
    
      \textbf{\href{http://www.software.ac.uk/}{Software Sustainability Institute}, UK}
  \begin{outerlist}
  \item[\textit{Fellow 2016}] \hfill \textbf{2016--2017}
  
  \begin{innerlist}
    \item    Received £3,000 grant funding for travel and organising workshops.
    \item  Organised training courses for: version control (git), Python.
    \item  Selected new fellows for 2017 and 2018.
  \end{innerlist}
  \end{outerlist}
  \vspace{15pt}
 
     \item Tutored on the Language and Cognition module.
    \item Ran and developed the Block Practical: \href{http://oliviaguest.com/connectionism}{Connectionist Models and Cognitive Processes}.

  \begin{innerlist}
    \item Taught on a range of courses within psychological sciences.
    \item Was trained to evaluate, mark, invigilate, and support part-time, mature, and full-time students.
    \item Managed the SONA system.
    %****will anyone know what SONA is?
    \item Organised and led the \href{http://cccm.bbk.ac.uk/}{Centre for Cognition, Computation and Modelling}'s  seminar. 
  \end{innerlist} 
  
  \paper{\textbf{Guest, O.} \& Love, B. C. (revise and resubmit). \href{https://dx.doi.org/10.1101/626374}{Levels of Representation in a Deep Learning Model of Categorization}. \textit{bioRxiv}. \href{https://doi.org/10.1101/626374}{doi.org/10.1101/626374}}{We demonstrate the utility of deep-neural network modelling in psychology via two case studies: (1) shape bias in infants, and (2) abstract category learning in pigeons}
