\documentclass[10pt]{article}
\usepackage{fontspec} 
\setmainfont{Lato}[Extension = .ttf,UprightFont = *-Light, BoldFont = *-Regular, SmallCapsFont = *-Light, ItalicFont = *-LightItalic]
\usepackage{calc}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Adapted from http://tex.stackexchange.com/a/4304/9668
\newcommand{\CC}{C\nolinebreak\hspace{.02em}+\nolinebreak\hspace{0.04em}+}

% Layout: Puts the section titles on left side of page
\reversemarginpar

\usepackage[paper=a4paper,
           includefoot, % Uncomment to put page number above margin
           marginparwidth=30.5mm,    % Length of section titles
           marginparsep=1.5mm,       % Space between titles and text
           margin=25mm,              % 25mm margins
           includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

\usepackage{eurosym}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
% \pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\definecolor{red}{HTML}{9B0E0E}


\hypersetup{colorlinks,breaklinks,
            linkcolor=red,urlcolor=red,
            anchorcolor=red,citecolor=red}

\usepackage{anyfontsize}
% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]{
\begin{center}\noindent\hspace{-16mm}{\fontsize{35}{60}{\selectfont{\scshape#1}}
\newcommand{\MONTH}{%
  \ifcase\the\month
  \or January% 1
  \or February% 2
  \or March% 3
  \or April% 4
  \or May% 5
  \or June% 6
  \or July% 7
  \or August% 8
  \or September% 9
  \or October% 10
  \or November% 11
  \or December% 12
  \fi}

\vspace{3mm}

\noindent\hspace{-16mm}\MONTH ~ \the\year }
\end{center}

\vspace{8pt}
}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \
         
         \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

\newcommand{\blankline}{\quad\pagebreak[2]}

\begin{document}
\makeheading{Olivia Guest}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONTACT}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}{.49\textwidth}
\begin{description}
 \item[Emails:] \href{mailto:o.guest@ucl.ac.uk}{o.guest@ucl.ac.uk}
%  \href{mailto:o.guest@rise.org.cy}{o.guest@rise.org.cy}
%  \href{mailto:contact@oliviaguest.com}{contact@oliviaguest.com}
 \item[Website:] \href{http://oliviaguest.com}{oliviaguest.com}
 \item[Blog:] \href{http://neuroplausible.com}{neuroplausible.com}
 \end{description}
\end{minipage}
\begin{minipage}{.49\textwidth}
\begin{description}
 \item[GitHub:] \href{https://github.com/oliviaguest}{oliviaguest}
 \item[Twitter:] \href{https://twitter.com/o_guest}{@o\textunderscore guest}
 \item[ORCID:] \href{http://orcid.org/0000-0002-1891-0972}{0000-0002-1891-0972}
 \end{description}
\end{minipage}
\vspace{8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CURRENT AFFILIATIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  \textbf{\href{https://rise.org.cy}{RISE}, Cyprus}
  \begin{outerlist}
  \item[\textbf{Research Centre on Interactive Media, Smart Systems and Emerging Technologies}]
  \item[\textit{Researcher}] \hfill \textbf{2019--}
  \end{outerlist}
  \vspace{15pt}
  
  \textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
  \item[\textbf{\href{https://bradlove.org/}{Prof. Bradley C. Love's Lab}}] 
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}

  \end{outerlist}
  \vspace{15pt}
  
  
  \textbf{School of Mathematics, Computer Science and Engineering, City, \newline University of London, UK}
  \begin{outerlist}
  \item[\textbf{\href{https://cit-ai.net}{CitAI, Artificial Intelligence Research Centre}}]
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}
  \end{outerlist}

  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PROFESSIONAL\texorpdfstring{\newline}{ }EXPERIENCE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \textbf{\href{https://rise.org.cy}{RISE}, Cyprus}
  \begin{outerlist}
  \item[\textbf{Research Centre on Interactive Media, Smart Systems and Emerging Technologies}]
  \item[\textit{Researcher}] \hfill \textbf{2019--}
    
  \begin{innerlist}
    \item  Funded by EU Horizon 2020 programme (grant 739578) and the Republic of Cyprus through the Directorate General for European Programmes, Coordination and Development.
    \item Researching deep neural network models with respect to face processing, conceptual organisation and alignment, and cognitive science generally. 
  \end{innerlist}
%   Carry out independent research on my own as well as in collaboration with other research groups, apply for grants, 
  
  \end{outerlist}
  
  \vspace{15pt}
  

\textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
  \item[\textbf{\href{https://bradlove.org/}{Prof. Bradley C. Love's Lab}}] 
  \item[\textit{Affiliated Researcher}] \hfill \textbf{2019--}
    \begin{innerlist}
    \item  Serving on hiring committees for postdoctoral fellows.
    \item  Assisting with Cognitive and Decision Sciences M.Sc.
    \item  Mentoring students and postdocs.

  \end{innerlist}
  \end{outerlist}
  \vspace{15pt}

\begin{samepage}

\textbf{\href{https://www.ucl.ac.uk/pals/research/experimental-psychology/}{Department of Experimental Psychology}, University College London, UK}
\begin{outerlist}
  \item[\textit{Postdoctoral Researcher}] \hfill \textbf{2016--2019}
  
  \begin{innerlist}
    \item  Created computational models: for categorisation, for model-based fMRI, used deep neural networks, etc.
    \item  Mentored Ph.D. and M.Sc. students (CSML and DSML M.Sc.s)
    \item  Organised training courses for: git, continuous integration, module testing.
    \item  Served on hiring committees for postdoctoral fellows.
    \item  Assisted with Cognitive and Decision Sciences M.Sc.
  \end{innerlist}
  \end{outerlist}
  \end{samepage}

  \vspace{15pt}

  \textbf{\href{http://www.software.ac.uk/}{Software Sustainability Institute}, UK}
  \begin{outerlist}
  \item[\textit{Fellow 2016}] \hfill \textbf{2016--2017}
  
  \begin{innerlist}
    \item    Received £3,000 grant funding for travel and organising workshops.
    \item  Organised training courses for: version control (git), Python.
    \item  Selected new fellows for 2017 and 2018.
  \end{innerlist}
  \end{outerlist}
  \vspace{15pt}
  
  \begin{samepage}
  \textbf{\href{http://www.psy.ox.ac.uk/}{Department of Experimental Psychology}, University of Oxford, UK}
  \begin{outerlist}
  \item[\textit{Postdoctoral Researcher}] \hfill \textbf{2014--2016}

  \begin{innerlist}
    \item Created models for category learning in infancy.
    \item Tutored on the Language and Cognition module.
    \item Ran and developed the Block Practical: \href{http://oliviaguest.com/connectionism}{Connectionist Models and Cognitive Processes}.
  \end{innerlist}
\end{outerlist}
  \vspace{15pt}
  \end{samepage}

\textbf{\href{http://www.bbk.ac.uk/psychology/}{Department of Psychological Sciences}, \href{http://www.bbk.ac.uk/}{Birkbeck}, UK}
\begin{outerlist}
  \item[\textit{Graduate Teaching Assistant}] \hfill \textbf{2010--2014}

  \begin{innerlist}
    \item Taught on a range of courses within psychological sciences.
    \item Was trained to evaluate, mark, invigilate, and support part-time, mature, and full-time students.
    \item Managed the SONA system.
    %****will anyone know what SONA is?
    \item Organised and led the \href{http://cccm.bbk.ac.uk/}{Centre for Cognition, Computation and Modelling}'s  seminar. 
  \end{innerlist}
\end{outerlist}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EDUCATION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{\href{http://www.bbk.ac.uk/}{Birkbeck}, UK} \hfill \textbf{2010--2014}
\begin{outerlist}
  \item[Ph.D., Psychological Sciences,] Sep 2014
  \begin{innerlist}
    \item Thesis: \emph{Towards a Unified Computational Account of Semantic Impairments}
    \item 1st Supervisor: \emph{Richard P. Cooper}
    \item 2nd Supervisor: \emph{Eddy J. Davelaar}
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.ucl.ac.uk/}{University College London}, UK} \hfill \textbf{2009--2010}
\begin{outerlist}
  \item[M.Sc., \href{http://www.ucl.ac.uk/lifesciences-faculty/degree-programmes/cognitive-decision-sciences}{Cognitive and Decision Sciences} (Distinction),] Sep 2010
  \begin{innerlist}
    \item Thesis: \emph{Modelling Semantic Memory \& Its Impairments Following Neural Damage}
    \item Supervisor: \emph{Richard P. Cooper}
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.york.ac.uk/}{The University of York}, UK} \hfill \textbf{2006--2009}
\begin{outerlist}
  \item[B.Sc., \href{http://www.cs.york.ac.uk/} {Computer Science},] Jun 2009
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{REVIEWING \& \protect\newline SERVICE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\begin{outerlist}
   \item[\textbf{\href{http://rescience.github.io/}{ReScience C Journal}} --- \textit{Editor-in-Chief}] \hfill \textbf{2020--}
   
   \item[\textbf{\href{https://joss.theoj.org/}{The Journal of Open Source Software}} --- \textit{Topic Editor}] \hfill \textbf{2019--}

   \item[\textbf{\href{http://rescience.github.io/}{ReScience C Journal}} --- \textit{Associate Editor}] \hfill \textbf{2015--2020}
   
 \item[\textbf{Conferences (ad hoc)}] \hfill
 
  International Conference on Cognitive Modelling (ICCM), International Conference on Machine Learning (ICML), Scientific Computing with Python Conference (SciPy).
  
   \item[\textbf{Journals (ad hoc)}] \hfill
    
    Cognitive Science Journal, Cognitive Psychology, Memory \& Cognition, PLoS Computational Biology, Journal of Cognitive Neuroscience.
    
   \item[\textbf{Special issue on \href{https://reproducibility-challenge.github.io/neurips2019/dates/}{NeurIPS 2019 Reproducibility Challenge}}] \hfill
   
   Co-editing special issue of Rescience C.

 \end{outerlist}

 
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PREPRINTS \& UNPUBLISHED}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \textbf{Guest, O.}, Martin, A. E., \& Birhane, A. (in prep.). {There is no such thing as AI}.
% \vspace{7.5pt}

% \textbf{Guest, O.} et al. (submitted to special issue). {Can ``open science'' make science open?}. \textit{Psychology of Women Quarterly}.
% \vspace{7.5pt}

Bobadilla Suarez, S., \textbf{Guest, O.}, \& Love, B. C. (revise and resubmit).  {The neural link between subjective value and decision entropy}. \textit{Communications Biology}.
\newline
\href{https://doi.org/10.1101/2020.02.18.954362}{doi.org/10.1101/2020.02.18.954362}
\vspace{7.5pt}

Barlas, P., Kyriakou, K., \textbf{Guest, O.}, Kleanthous, S., \& Otterbacher, J. (in prep). {Social B(eye)as Dataset v2.0: Automatically Tagging People Images in Context}.
\vspace{7.5pt}

Barlas, P., Kyriakou, K., \textbf{Guest, O.}, Kleanthous, S., \& Otterbacher, J. (in prep). {A ``Woman's Place'' is Nowhere: Image Tagging Algorithms Overlook Women Even in Stereotypically Feminine Contexts}.
\vspace{7.5pt}

\textbf{Guest, O.} \& Martin, A. E. (under review, invited to special issue).  \href{https://doi.org/10.31234/osf.io/rybh9}{How computational modeling can force theory building in psychological science}. \textit{Perspectives on Psychological Science}. \href{https://doi.org/10.31234/osf.io/rybh9}{doi.org/10.31234/osf.io/rybh9}
\vspace{7.5pt}

Whitaker, K. J. \& \textbf{Guest, O.} (invited, in press).  {\#bropenscience is broken science}. \textit{The Psychologist}.
\vspace{7.5pt}

\textbf{Guest, O.} \& Love, B. C. (2019). \href{https://dx.doi.org/10.1101/626374}{Levels of Representation in a Deep Learning Model of Categorization}. \textit{bioRxiv}. \href{https://doi.org/10.1101/626374}{doi.org/10.1101/626374}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PUBLICATIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Guest, O.}, Caso A. \& Cooper, R. P. (2020, in press).  {On Simulating Neural Damage in Connectionist Networks}. \textit{Computational Brain \& Behavior}
 \href{https://doi.org/10.1007/s42113-020-00081-z}{doi.org/10.1007/s42113-020-00081-z}
\vspace{7.5pt}

Botvinik-Nezer, R. et al. (2020). \href{https://doi.org/10.1038/s41586-020-2314-9}{Variability in the analysis of a single neuroimaging dataset by many teams}. \textit{Nature}. \href{https://doi.org/10.1038/s41586-020-2314-9}{doi.org/10.1038/s41586-020-2314-9}
\vspace{7.5pt}


\textbf{Guest, O.}, Kanayet, F. J., \& Love, B. C. (2019). \href{https://dx.doi.org/10.1007/s42001-019-00053-9}{Gerrymandering and Computational Redistricting}. \textit{Journal of Computational Social Science}. 
\href{https://dx.doi.org/10.1007/s42001-019-00053-9}{doi.org/10.1007/s42001-019-00053-9}
\vspace{7.5pt}

Rougier, N. P. et al. (2017). \href{http://dx.doi.org/10.7717/peerj-cs.142}{Sustainable computational science: the ReScience initiative}. \textit{PeerJ Computer Science}. \href{http://dx.doi.org/10.7717/peerj-cs.142}{doi.org/10.7717/peerj-cs.142}  
\vspace{7.5pt}

Love, B. C., \textbf{Guest, O.}, Slomka, P., Navarro, V., Wasserman, E. (2017). \href{https://mindmodeling.org/cogsci2017/papers/0283/index.html}{Deep Networks as Models of Human and Animal Categorization}. \textit{In Proceedings of the 39th Annual Meeting of	the	Cognitive Science	Society}. (pp. 1457--1458).
\vspace{7.5pt}

\textbf{Guest, O.} \& Love, B. C. (2017). \href{http://dx.doi.org/10.7554/eLife.21397}{What the Success of Brain Imaging Implies about the Neural Code}. \textit{eLife}, 6:e21397.
\href{http://dx.doi.org/10.7554/eLife.21397}{doi.org/10.7554/eLife.21397}
\vspace{7.5pt}

\textbf{Guest, O.} \& Rougier, N. P. (2016). \href{https://oliviaguest.com/doc/guest_rougier_2016.pdf}{What is computational reproducibility?} \textit{IEEE CIS Newsletter on Cognitive and Developmental Systems}, 13 (1).
\vspace{7.5pt}

\textbf{Guest, O.} (2016). \href{http://dx.doi.org/10.15200/winn.146590.01538}{Crisis in What Exactly?}. \textit{The Winnower}. \newline
\href{http://dx.doi.org/10.15200/winn.146590.01538}{doi.org/10.15200/winn.146590.01538}
\vspace{7.5pt}

Love, B. C., Kopeć, Ł. \& \textbf{Guest, O.} (2015). \href{http://dx.doi.org/10.1371/journal.pone.0137685}{Optimism Bias in Fans and Sports Reporters}. \textit{PLoS ONE}, 10 (9).
\href{http://dx.doi.org/10.1371/journal.pone.0137685}{doi.org/10.1371/journal.pone.0137685}
\vspace{7.5pt}

Cooper, R. P. \& \textbf{Guest, O.} (2014).  \href{http://dx.doi.org/10.1016/j.cogsys.2013.05.001}{Implementations are not specifications: specification, replication and experimentation in computational cognitive modeling}. \textit{Cognitive Systems Research}, 27, 42--49.
\href{http://dx.doi.org/10.1016/j.cogsys.2013.05.001}{doi.org/10.1016/j.cogsys.2013.05.001}
\vspace{7.5pt}

\textbf{Guest, O.}, Cooper, R. P. \& Davelaar, E. J. (2014).  [High-Level Cognition]. \href{http://oliviaguest.com/doc/guest_14.pdf}{The Influence of Implementation on ``Hub'' Models of Semantic Cognition}. In J. Mayor, P. Gomez (Eds.), \textit{\href{http://www.worldscientific.com/worldscibooks/10.1142/8747}{Computational Models of Cognitive Processes}} (pp. 155--169). World Scientific.
\vspace{7.5pt}

\begin{samepage}

\textbf{Guest, O.}, Cooper, R. P. \& Davelaar, E. J. (2012). \href{http://eprints.bbk.ac.uk/6758/}{Semantic Cognition: A Re-examination of the Recurrent Network ``Hub'' Model}. \textit{In Proceedings of the Ninth International Conference on Cognitive Modelling.} Berlin, Germany. April. (pp. 259--264). Berlin, Germany. April. Universit\"{a}tsverlag der TU Berlin.

\end{samepage}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INVITED\texorpdfstring{\newline}{ }TALKS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{\href{}{Bordeaux-Sud-Ouest Inria Research Centre}} 
\begin{outerlist}
  \item[] \textit{Bordeaux, France}\hfill\textbf{21--22 Sep 2020}
  \begin{innerlist}
    \item Talk (TBD): \textit{How computational modeling can force theory building in psychological science}
    \item Organiser: Nicolas P. Rougier


  \end{innerlist}
\end{outerlist}
\vspace{8pt}


\textbf{\href{https://www.eventbrite.co.uk/o/reproducibilitea-ucl-19116673509}{ReproducibiliTea UCL}} 
\begin{outerlist}
  \item[] \textit{UCL, UK}\hfill\textbf{14 Sep 2020}
  \begin{innerlist}
    \item Talk: \textit{How computational modeling can force theory building in psychological science}
    \item Organiser: Emma Norris, Tabea Schoeler, \&  Jessie Baldwin

  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://mathpsych.org/conferences/2020/}{MathPsych/ICCM 2020}} 
\begin{outerlist}
  \item[] \textit{Toronto, Canada}\hfill\textbf{25--28 Jul 2020}
  \begin{innerlist}
    \item Symposium: \textit{Perspectives on ``What makes a good theory?''}
    \item Organisers: Iris van Rooij \& Chris Donkin 


  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{https://www.kcl.ac.uk/events/series/riot-science-club}{RIOT Science Club}} 
\begin{outerlist}
  \item[] \textit{King's College London, London, UK}\hfill\textbf{2 Jul 2020}
  \begin{innerlist}
    \item Talk (TBD): \textit{How computational modeling can force theory building in psychological science}
    \item Organiser: Miguel Xochicale


  \end{innerlist}
\end{outerlist}
\vspace{8pt}


\textbf{\href{https://github.com/annahensch/Glasgow-ReproducibiliTea}{ReproducibiliTea Glasgow}} 
\begin{outerlist}
  \item[] \textit{Univeristy of Glasgow, UK}\hfill\textbf{20 Apr 2020}
  \begin{innerlist}
    \item Talk: \textit{\href{https://www.youtube.com/watch?v=_WV7EFvFAB8}{How computational modeling can force theory building in psychological science}}
    \item Organisers: Anna Henschel \& Stephanie Allan
    \item Speakers: Olivia Guest \& Andrea E. Martin


  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.rise.org.cy/en-gb/}{Research Centre on Interactive Media, Smart Systems and Emerging Technologies}}
\begin{outerlist}
  \item[] \textit{Nicosia, Cyprus}\hfill\textbf{16 Jul 2019}
  \begin{innerlist}
    \item Talk: \textit{\href{https://dx.doi.org/10.1101/626374}{What do deep neural networks know?}}
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\begin{samepage}
\textbf{\href{https://icml.cc}{Thirty-fifth International Conference on Machine Learning (ICML 2018)}}
\newline Workshop: \href{https://mltrain.cc/events/enabling-reproducibility-in-machine-learning-mltrainrml-icml-2018/}{Enabling Reproducibility in Machine Learning MLTrain@RML}
\begin{outerlist}
  \item[] \textit{Stockholm, Sweden}\hfill\textbf{14 Jul 2018}
  \begin{innerlist}
    \item Talk:  \textit{\href{https://figshare.com/articles/Varieties_of_Reproducibility_in_Empirical_and_Computational_Domains/6818018}{Varieties of Reproducibility in Empirical and Computational Domains}}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}
\end{samepage}

\textbf{\href{http://opendataday.org/}{Open Data Day 2018}}
\begin{outerlist}
  \item[] \textit{Goldsmiths, University of London, UK}\hfill\textbf{3 Mar 2018}
  \begin{innerlist}
    \item Talk:  \textit{\href{http://figshare.com/articles/Gerrymandering_and_Computational_Redistricting/5605387}{Gerrymandering and Computational Redistricting}}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{https://psychology.stanford.edu/events/frisem}{Cognitive Neuroscience Friday Seminar (FriSem)}}
\begin{outerlist}
  \item[] \textit{Stanford University, California, USA}\hfill\textbf{16 Feb 2018}
  \begin{innerlist}
    \item Talk: \textit{How deep networks contribute to our understanding of human and animal representation in categorization}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.ucl.ac.uk/research-it-services/research-software-development/programming-hub/tech-socials}{Research Programming Technical Social}}
\begin{outerlist}
  \item[] \textit{University College London, UK}\hfill\textbf{15 Nov 2017}
  \begin{innerlist}
    \item Talk: \textit{\href{https://figshare.com/articles/Gerrymandering_and_Computational_Redistricting/5605387/3}{Gerrymandering and Computational Redistricting}}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.ru.nl/cls/}{Centre for Language Studies}}
\begin{outerlist}
  \item[] \textit{Radboud University, The Netherlands}\hfill\textbf{8 Mar 2017}
  \begin{innerlist}
    \item Talk: \textit{\href{https://figshare.com/articles/What_the_Success_of_Brain_Imaging_Implies_about_the_Neural_Code/4252022}{What the Success of Brain Imaging Implies about the Neural Code}}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://ljdm.info}{London Judgement and Decision Making Seminars}}
\begin{outerlist}
  \item[] \textit{University College London, UK}\hfill\textbf{8 Feb 2017}
  \begin{innerlist}
    \item Talk: \textit{\href{https://figshare.com/articles/What_the_Success_of_Brain_Imaging_Implies_about_the_Neural_Code/4252022}{What the Success of Brain Imaging Implies about the Neural Code}}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://decisions.psy.ox.ac.uk/}{Summerfield Lab}}
\begin{outerlist}
  \item[] \textit{University of Oxford, UK}\hfill\textbf{23 Nov 2016}
  \begin{innerlist}
    \item Talk: \textit{\href{https://figshare.com/articles/What_the_Success_of_Brain_Imaging_Implies_about_the_Neural_Code/4252022}{What the Success of Brain Imaging Implies about the Neural Code}}.
  \end{innerlist}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONFERENCE \texorpdfstring{\newline}{ } PRESENTATIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{\href{https://www.sfn.org/meetings/neuroscience-2019}{Society for Neuroscience (SfN 2019)}}
\begin{outerlist}
  \item[] \textit{Chicago, USA}\hfill\textbf{19--23 Oct 2019}
  \begin{innerlist}
    \item Poster: \textit{The neural link between subjective value and decision entropy}.
    \item{Presented by: S. Bobadilla Suarez}
  \end{innerlist}
\end{outerlist}
\vspace{8pt}



\textbf{\href{https://www.cancyprus.org/wp-content/uploads/2019/10/Conference-Booklet-2019-print.pdf}{9th Annual Scientific Conference of Center for Applied Neuroscience}}
\begin{outerlist}
  \item[] \textit{Nicosia, Cyprus}\hfill\textbf{4 Oct 2019}
  \begin{innerlist}
    \item Talk and poster:  \textit{Levels of Representation in a Deep Learning Model of Categorization}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.cogs.indiana.edu/asic/2019/index.shtml}{18th Annual Summer Interdisciplinary Conference (ASIC 2019)}}
\begin{outerlist}
  \item[] \textit{Seefeld, Austria}\hfill\textbf{17--22 Jun 2019}
  \begin{innerlist}
    \item Talk: \textit{Levels of Representation in a Deep Learning Model of Categorization}.
  \end{innerlist}
\end{outerlist}
\begin{samepage}

\textbf{\href{http://www.cognitivesciencesociety.org/conference/cogsci2017/}{ 39th Annual Meeting of the Cognitive Science Society (CogSci 2017)}}
\begin{outerlist}
  \item[] \textit{London, UK}\hfill\textbf{26--29 Jul 2017}
  \begin{innerlist}
    \item Talk: \textit{Deep Networks as Models of Human and Animal Categorization}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}\end{samepage}

\begin{samepage}

\textbf{\href{http://www.cogs.indiana.edu/asic/2017/index.shtml}{16th Annual Summer Interdisciplinary Conference (ASIC 2017)}}
\begin{outerlist}
  \item[] \textit{Interlaken, Switzerland}\hfill\textbf{15--20 Jul 2017}
  \begin{innerlist}
    \item Talk: \textit{Deep Networks as Models of Human and Animal Categorization}.
  \end{innerlist}
\end{outerlist}

\vspace{8pt}\end{samepage}

\textbf{\href{http://wp.lancs.ac.uk/lcicd/past-events/}{1st Lancaster Conference on Infant and Early Child Development (LCICD 2016)}}
\begin{outerlist}
  \item[] \textit{Lancaster, UK}\hfill\textbf{25--27 Aug 2016}
  \begin{innerlist}
    \item Talk: \textit{Representational Re-description in hSOMs}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.cogs.indiana.edu/asic/2016/index.shtml}{15th Annual Summer Interdisciplinary Conference (ASIC 2016)}}
\begin{outerlist}
  \item[] \textit{Selva, Val Gardena, Italy}\hfill\textbf{3--8 Jul 2016}
  \begin{innerlist}
    \item Talk: \textit{What the Success of Brain Imaging Implies about the Neural Code}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.cogs.indiana.edu/asic/2015/index.shtml}{14th Annual Summer Interdisciplinary Conference (ASIC 2015)}}
\begin{outerlist}
  \item[] \textit{Mammoth Lakes, California, USA}\hfill\textbf{10--15 Jul 2015}
  \begin{innerlist}
    \item Talk: \textit{Optimism Bias in Novice and Expert Sport Forecasting}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.bcbl.eu/events/ncpw13/}{13th Neural Computation and Psychology Workshop (NCPW 13)}}
\begin{outerlist}
  \item[] \textit{\href{http://www.bcbl.eu/}{BCBL}, San Sebastian, Spain}\hfill\textbf{12--14 Jul 2012}
  \begin{innerlist}
    \item Talk: \textit{Exploring the influence of architecture and learning algorithm on the breakdown of the ``hub'' model of semantic cognition}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://iccm-conference.org/2012/}{11th International Conference on Cognitive Modeling (ICCM 2012)}}
\begin{outerlist}
  \item[] \textit{\href{http://www.tu-berlin.de/menue/home/parameter/en/}{Technische Universit\"{a}t Berlin}, Berlin, Germany}
  \hfill \textbf{12--15 Apr 2012}
  \begin{innerlist}
    \item Poster: \textit{Semantic Cognition: A Re-examination of the Recurrent Network ``Hub'' Model}.
    \item Won Best Student Poster Prize.
  \end{innerlist}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ORGANISING}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\textbf{\href{https://scipy2019.scipy.org}{18th Scientific Computing with Python Conference (SciPy 2019)}}
\begin{outerlist}
  \item[] \textit{Austin, Texas, USA} \hfill \textbf{8--14 Jul 2019}
  \begin{innerlist}
    \item \href{https://www.eiseverywhere.com/ehome/381993}{Chaired cognitive science and neuroscience mini-symposium} with \href{https://www.labri.fr/perso/nrougier/}{Nicolas P. Rougier}.
    \item Reviewed conference submissions.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://womenincogsci.org/announcement/wics-workshop-cognitive-science-society-meeting-madison-wisconsin}{Women in Cognitive Science (WiCS) Panel at 40th Annual Meeting of the Cognitive Science Society (CogSci 2018)}}
\begin{outerlist}
  \item[] \textit{Madison, Wisconsin, USA} \hfill \textbf{25 Jul 2018}
  \begin{innerlist}
    \item Topic: Women and Gender Minorities in Computational Cognitive Science: Sharing Experiences.
    \item Co-organised with Nora S. Newcombe.
    % \item Panel members: Eliana Colunga, Amy Perfors, and myself.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}
\begin{samepage}

\textbf{\href{https://scipy2017.scipy.org}{16th Scientific Computing with Python Conference (SciPy 2017)}}
\begin{outerlist}
  \item[] \textit{Austin, Texas, USA} \hfill \textbf{10--16 Jul 2017}
  \begin{innerlist}
    \item \href{https://scipy2017.scipy.org/ehome/220975/493433/}{Chaired neuroscience mini-symposium} with \href{http://arokem.org/}{Ariel Rokem}.
    \item Reviewed conference submissions.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}\end{samepage}

\begin{samepage}

\textbf{\href{http://www.software.ac.uk/rdvw/}{Research Data Visualisation Workshop (RDVW)}}
\begin{outerlist}
  \item[] \textit{\href{http://software.ac.uk/}{Software Sustainability Institute}, \href{http://www.manchester.ac.uk/}{University of Manchester}} \hfill \textbf{28 Jul 2016}
  \begin{innerlist}
    \item Organised 1-day workshop with \href{http://www.software.ac.uk/about/people/raniere-silva}{Raniere Silva} (main organiser) and \href{http://www.cardiff.ac.uk/people/view/98654-knight-vincent}{Vince Knight}.
    \item Member of \href{http://www.software.ac.uk/rdvw/committees}{steering committee}.
    \item Obtained funding from \href{https://www.rstudio.com/}{RStudio}.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}
\end{samepage}

\textbf{\href{https://sites.google.com/site/introcompcog/}{Introduction to Computational Cognitive Modelling Workshop}}
\begin{outerlist}
  \item[] \textit{\href{http://cccm.bbk.ac.uk/}{CCCM}, Birkbeck}         \hfill \textbf{23--25 Apr 2014}
  \begin{innerlist}
     \item Organised 3-day workshop with \href{https://www.researchgate.net/profile/Chris_Brand}{Chris Brand} (co-organiser).
     \item Prepared slides, exercises, created website.
  \end{innerlist}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{TEACHING}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{\href{http://www.psy.ox.ac.uk/}{Department of Experimental Psychology}, \href{http://ox.ac.uk/}{University of Oxford}, UK}
\begin{outerlist}
    \item[Postdoctoral Research Assistant] \hfill \textbf{2014--2016}
    \item[\textit{\href{http://oliviaguest.com/connectionism}{Block Practical: Connectionist Models and Cognitive Processes}}] \
  \begin{innerlist}
    \item Module: \textit{Third Year, B.Sc.}
    \item Designed course structure and materials (slides and exercises).
    \item Set final report wherein students replicated from scratch Tyler et al. (2000) in Python.
    \item Created course website: \href{http://oliviaguest.com/connectionism}{oliviaguest.com/connectionism}.
  \end{innerlist}
      \item[\textit{Tutorial: Language and Cognition}] \
  \begin{innerlist}
    \item Module: \textit{Second Year, B.Sc.}
    \item Set essays and marked exams.
  \end{innerlist}
\end{outerlist}
\vspace{8pt}

\textbf{\href{http://www.bbk.ac.uk/psychology/}{Department of Psychological Sciences}, \href{http://www.bbk.ac.uk/}{Birkbeck, University of London},
UK}
\begin{outerlist}
   \item[Graduate Teaching Assistant] \hfill \textbf{2010--2014}
   \item Modules Taught: \textit{General Foundations of Psychology,
   Psychobiology, Advanced Research Methods, Advanced Quantitative Methods, Memory and Cognition, Matlab Programming for Psychological Science, }
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MAINSTREAM MEDIA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}


\begin{outerlist}
 \item[\textbf{\href{https://dx.doi.org/10.1007/s42001-019-00053-9}{Gerrymandering and computational redistricting}}] \hfill\textbf{2017}
\begin{innerlist}
	\item Media Coverage: \href{https://www.seeker.com/tech/an-unbiased-algorithm-could-help-put-an-end-to-partisan-gerrymandering}{\textit{An Unbiased Algorithm Could Help Put an End to Partisan Gerrymandering}}, Seeker
\end{innerlist}

 \item[\textbf{\href{http://www.bbc.co.uk/radio4}{BBC Radio 4:}} \href{http://www.bbc.co.uk/programmes/b0713zdz}{Today Show}] \hfill\textbf{2016}
\begin{innerlist}
	\item Interview: \textit{What can we learn in 4 months?}
\end{innerlist}

\item[\textbf{\href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0137685}{Optimism Bias in Fans and Sports Reporters}}] \hfill\textbf{2015}
\begin{innerlist}
  \item Press Releases: \href{http://www.ox.ac.uk/news/2015-09-09-nfl-fans-and-espn-reporters-overly-optimistic-about-team-prospects}{University of Oxford}, \href{https://www.ucl.ac.uk/news/news-articles/0915/100915-nfl-team-prospects}{UCL}
  \item Media Coverage: \href{http://www.csmonitor.com/Science/2015/0909/NFL-scores-Your-team-is-probably-less-invincible-than-you-imagine}{CS Monitor},
  \href{http://www.medicaldaily.com/rose-colored-glasses-nfl-fans-and-sports-reporters-overestimate-how-good-their-teams-351888}{Medical Daily},
  \href{https://www.minnpost.com/second-opinion/2015/09/why-football-fans-are-unrealistically-optimistic-and-why-it-matters}{MinnPost},
  \href{http://europe.newsweek.com/nfl-fans-and-reporters-overly-optimistic-about-teams-prospects-332758}{Newsweek},
  \href{http://www.psmag.com/health-and-behavior/this-study-explains-why-raiders-fans-continue-going-to-watch-their-team-play}{Pacific Standard},
  \href{http://phys.org/news/2015-09-nfl-fans-espn-overly-optimistic.html}{Phys.org}. 
\end{innerlist}
\end{outerlist}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{TECHNICAL\texorpdfstring{\newline}{ }SKILLS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\begin{outerlist}
 \item[\textbf{General}] \hfill
 \begin{innerlist}
   \item  Web design (e.g., \href{http://bradlove.org}{bradlove.org}, \href{http://neuroplausible.com}{neuroplausible.com}, \href{http://oliviaguest.com}{oliviaguest.com}, \href{http://redistrict.science}{redistrict.science}, \href{http://compcog.science}{compcog.science}).
 \item Graphic design and image editing (i.e., Adobe Suite, GIMP, Inkscape).
 \item GUI design (i.e., PyGTK, GTK+).
 \item Artificial neural networks (e.g., TensorFlow).
 \item Unix (e.g., CLI, server administration).
 \end{innerlist}
 \item[\textbf{Programming}] \hfill
 
Ada, C, \CC, C\#, Java, JavaScript, \LaTeX, MATLAB,  OpenGL, Pascal, PHP, Prolog, Python, R, Scheme, SQL, Visual Basic.
 \end{outerlist}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{LANGUAGES}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-10pt}

% \begin{description}
%  \item[Native:] Modern Greek, Cypriot Greek, English
%   \item[Basic:] French, Italian
%  \end{description}
\end{document}
% %%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
